\begin{itemize}
\item[\Large $\dagger$] {\Large \textbf{List of Abbreviations}}
    \begin{enumerate}
    \item[$\cdot$] {CLIP : Contrastive language-image pre-training.}
    \item[$\cdot$] {CNN : Convolutional neural network.}
    \item[$\cdot$] {CPU : Central processing unit.}
    \item[$\cdot$] {DCN : Deformable convolutions.}
    \item[$\cdot$] {DDPM : Denoising diffusion probabilistic model.}
    \item[$\cdot$] {DISTS : Deep image structure and texture similarity.}
    \item[$\cdot$] {DT-CWT : Dual-tree complex wavelet transform.}
    \item[$\cdot$] {DWT : Discrete wavelet transform.}
    \item[$\cdot$] {GAN : Generative adversarial network.}
    \item[$\cdot$] {GPU : Graphics processing unit.}
    \item[$\cdot$] {HR : High-resolution.}
    \item[$\cdot$] {LDM : Latent diffusion model.}
    \item[$\cdot$] {LPIPS : Learned perceptual image patch similarity.}
    \item[$\cdot$] {LR : Low-resolution.}
    \item[$\cdot$] {MSE : Mean squared error.}
    \item[$\cdot$] {MUSIQ : Multi-scale image quality transformer.}
    \item[$\cdot$] {NIQE : Natural image quality evaluator.}
    \item[$\cdot$] {OS : Operating system.}
    \item[$\cdot$] {PSNR : Peak signal-to-noise ratio.}
    \item[$\cdot$] {RAFT : Recurrent all-pairs field transforms.}
    \item[$\cdot$] {RNN : Recurrent neural network.}
    \item[$\cdot$] {SD : Stable diffusion.}
    \item[$\cdot$] {SFT : Spatial feature transform.}
    \item[$\cdot$] {SSIM : Structural similarity index measure.}
    \item[$\cdot$] {tLPIPS : Temporal learned perceptual image patch similarity.}
    \item[$\cdot$] {tOF : Temporal optical flow.}
    \item[$\cdot$] {VAE : Variational autoencoder.}
    \item[$\cdot$] {VSR : Video super-resolution.}
    \end{enumerate}
\end{itemize}