\newpage
\pagestyle{empty}
%\lhead{\bfseries RESEARCHES \& PUBLICATIONS}
%\chead{}
%\rhead{\thepage}
\begin{itemize}
\item[\Large $\dagger$] {\Large \textbf{Research Interests}}
\end{itemize}
\normalsize
\begin{itemize}
    \item[$\triangleright$] Deep learning for Facial Expression Recognition.
    \item[$\triangleright$] Deep learning for image classification.
    \item[$\triangleright$] Machine learning for computer vision.
\end{itemize}
\begin{itemize}
\vspace*{0.7cm} \item[\Large $\dagger$] {\Large \textbf{Funded Research Career}}
\end{itemize}
\normalsize
\begin{itemize}
    % \item[$\triangleright$] 초실감 테라미디어를 위한 AV부호화 및 LF미디어 원천기술 개발, 202saldifjawef, (ETRI)
    \item[$\triangleright$] Evaluation of Speech Recognition on Foreign Language Education Services in Online Video Platform Environment, Sep. 2022 $\sim$ Aug. 2023, Voice Print
    \item[$\triangleright$] Development of deep Learning based vision inspection system for bamboo toothbrush, July. 2021 $\sim$ Aug. 2022, Dr. NOAH
\end{itemize}
 \clearpage
\begin{itemize}
 \item[\Large $\dagger$] {\Large
\textbf{List of Publications}}
\end{itemize}


\vspace*{0.3cm}
\begin{center}
$\triangleright$ \large{\bf{International Journal}}
$\triangleleft$
\end{center}
\begin{itemize}
\normalsize 
\item \underline{C. L. Kim}, B. G. Kim*, “Few-shot Learning on Facial Expression Recognition: A Comprehensive Survey,” \textit{Journal of Real-Time Image Processing (Springer Nature)}, vol. 20:52 (Article number: 52), pp. 1-18.





\end{itemize}

\vspace*{0.5cm}
\begin{center}
$\triangleright$ \large{\bf{International Conference}}
$\triangleleft$
\end{center}
\begin{itemize}
\normalsize
\item Y. J. Kim, \underline{C. L. Kim}, H. L. Lee and B. G. Kim*, “Recent Trend for Monocular Depth Estimation Based on Deep Learning,” \textit{The 18th International Conference on Multimedia Information Technology and Applications (MITA)}, pp. 103-105, July. 2022 (*Best Paper Award*).
\end{itemize}


\vspace*{0.5cm}
\begin{center}
$\triangleright$ \large{\bf{Domestic Conference}}
$\triangleleft$
\end{center}
\begin{itemize}
\item H. L. Lee, \underline{C. L. Kim}, B. G. Kim*, and G. H Kim, “Integrated System for Facial Alignment and Lip Generation”, KMMS Spring Conference (KMMS), vol. 26, no. 1, pp. 77-78, May. 2023.
\end{itemize}

%domestic conference 2
\begin{itemize}
\item \underline{C. L. Kim}, Y. J. Choi, B. G. Kim*, E. H. Park, K. T. Lee “A Study of the Fault Detection Technique for the Bamboo Toothbrush Manufacturing Automation”, KMMS Autumn Conference (KMMS), vol. 24, no. 2, pp. 14-17, Nov. 2021.
\end{itemize}



%domestic conference 3
\begin{itemize}
\item \underline{C. L. Kim}, J. B. Seo, and B. G. Kim* “Development of Real-time Dangerous Situation Detection Algorithm Based on Object Detection and Depth Information Fusion”, KMMS Spring Conference (KMMS), vol. 24, no. 1, pp. 565-567, April. 2021.
\end{itemize}


